### 2019-05-19 README.rmd
fixing issue with badges

<!-- Package Review -->
[![](https://badges.ropensci.org/164_status.svg)](https://github.com/ropensci/onboarding/issues/164)
[![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)

>>>>

<!-- Package Review -->
[![](https://badges.ropensci.org/300_status.svg)](https://github.com/ropensci/onboarding/issues/300)
[![status](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6/status.svg)](http://joss.theoj.org/papers/334d80d5508056dc6e7e17c6fd3ed5a6)
